Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-10 inc/conclusions.tex
more work on conclusion, possibly complete through the model section (not model results)

>>>>

I have written an implementation of this model for the Perl programming language and released to the Comprehensive Perl Archive Network (CPAN) under the name \verb!Physics::UEMColumn! for use by the UEM community (\url{https://metacpan.org/module/Physics::UEMColumn}).
This model is fully object-oriented, which makes writing simulations remarkably easy for a user to read, write and change scripts.
Under the hood, though, it uses a custom set of C level bindings to the GNU Scientific Library (GSL), so that the numerical equation solving is fast and accurate.
I have found that this speed, combined with the dynamic flexibility offered by object-oriented Perl, has allowed me to easily write optimization scripts and generate figures which might have been nearly impossible previously; several of these have been shown in this thesis.
